\thetitle

### 2020-11-30 sun_phases/spin_qudit_tomo.tex
fixed minor error concerning the phase-spase representation of polarization operators

As a final point, we mention that the polarization operators $T_{\ell m}$ share a connection to the spherical harmonics $Y_{\ell m}$ that goes beyond the rules for their transformation under 3D rotations.
In fact, the phase-space (Wigner function) representation of $T_{\ell m}$ is essentially equal to $Y_{\ell m}$, up to complex conjugation and a normalization factor.
The phase-space representation of an operator $X$ assigns, to each point $\v v$ on the sphere, the complex number
\begin{align}
  \tilde X\p{\v v} \equiv \bk{s_{\v v}|X|s_{\v v}},
\end{align}
where $\ket{s_{\v v}}\equiv R\p{\v v}\ket{s}$ is the state of a spin qudit polarized along $\v v$.
This representation is faithful in the sense that $X$ is uniquely determined by the phase-space values $\tilde X\p{\v v}$ at all points $\v v$ on the sphere.
The transformation rules for polarization operators in Eq.~\eqref{eq:trans_rot}, together with the fact that $\bk{s|T_{\ell m}|s}=0$ unless $m=0$, suffice to show that their phase-space distributions are (see Appendix \ref{sec:rotations})
\begin{align}
  \tilde T_{\ell m}\p{\v v} = c_\ell Y_{\ell m}\p{\v v}^*,
\end{align}
where the scalar $c_\ell$ simply enforces that $\obk{T_{\ell m}|T_{\ell m}}=1$.
In this way, the polarization operators $T_{\ell m}$ are a quantum analogue of spherical harmonics $Y_{\ell m}$, which play an important role in phase-space formalisms for spin qudits \cite{li2013weylwignermoyal}.

@@

Implicitly associating the Euler angle doublet $\v v = \p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, the transformation rules in Eq.~\eqref{eq:trans_rot_apndx} imply that we can expand the phase-space distribution of $T_{\ell m}$ as
\begin{align}
  \tilde T_{\ell m}\p{\v v}
  \equiv \bk{s_{\v v} | T_{\ell m} | s_{\v v}}
  = \bk{s | R\p{\v v}^\dag T_{\ell m} R\p{\v v} | s}
  = D^\ell_{0,m}\p{\v v} \bk{s | T_{\ell,0} | s},
\end{align}
where
\begin{align}
  \bk{s | T_{\ell,0} | s}
  = \sqrt{\f{2\ell+1}{2s+1}} \, \bk{ss;\ell,0|ss}
  = \sqrt{\f{2\ell+1}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}}
    \p{\f{\p{2s}!}{\p{2s-\ell}!}}},
\end{align}
and the properties of the rotation matrix elements $D^\ell_{mn}$ imply that
\begin{align}
  D^\ell_{0,m}\p{\v v} = \p{-1}^m D^\ell_{-m,0}\p{\v v}^*
  = \sqrt{\f{4\pi}{2\ell+1}} \p{-1}^m Y_{\ell,-m}\p{\v v}
  = \sqrt{\f{4\pi}{2\ell+1}} \, Y_{\ell m}\p{\v v}^*,
\end{align}
so
\begin{align}
  \tilde T_{\ell m}\p{\v v}
  = \sqrt{\f{4\pi}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}} \p{\f{\p{2s}!}{\p{2s-\ell}!}}} \,
  Y_{\ell m}\p{\v v}^*
  \propto Y_{\ell m}\p{\v v}^*.
\end{align}
In this way, the polarization operators are a quantum analogue of spherical harmonics.

>>>>

As a final point, we mention that the polarization operators $T_{\ell m}$ share a connection to the spherical harmonics $Y_{\ell m}$ that goes beyond the rules for their transformation under 3D rotations.
In fact, the phase-space (Wigner function) representation of $T_{\ell m}$ is proportional to $Y_{\ell m}$.
The phase-space representation of a spin qudit operator $X$ assigns, to each point $\v v$ on the sphere, the number
\begin{align}
  X^{\t{PS}}\p{\v v} \equiv \bk{s_{\v v}|X|s_{\v v}},
\end{align}
where $\ket{s_{\v v}}\equiv R\p{\v v}\ket{s}$ is the state of a spin qudit polarized along $\v v$.
This representation is faithful in the sense that $X$ is uniquely determined by the phase-space values $X^{\t{PS}}\p{\v v}$ at all points $\v v$ on the sphere.
The transformation rules for polarization operators in Eq.~\eqref{eq:trans_rot}, together with the fact that $\bk{s|T_{\ell m}|s}=0$ unless $m=0$, suffice to show that (see Appendix \ref{sec:rotations})
\begin{align}
  T_{\ell m}^{\t{PS}}\p{\v v} = c_\ell Y_{\ell m}\p{\v v},
\end{align}
where the scalar $c_\ell$ simply enforces that $\obk{T_{\ell m}|T_{\ell m}}=1$.
The polarization operators $T_{\ell m}$ are a quantum analogue of spherical harmonics $Y_{\ell m}$, which play an important role in phase-space formalisms for spin qudits \cite{li2013weylwignermoyal}.

@@

Implicitly associating the Euler angle doublet $\v v = \p{\alpha,\beta}$ with the triplet $\p{\alpha,\beta,0}$, the transformation rules in Eq.~\eqref{eq:trans_rot_apndx} imply that we can expand the phase-space distribution of $T_{\ell m}$ as
\begin{align}
  \tilde T_{\ell m}\p{\v v}
  \equiv \bk{s_{\v v} | T_{\ell m} | s_{\v v}}
  = \bk{s | R\p{\v v}^\dag T_{\ell m} R\p{\v v} | s}
  = D^\ell_{0,m}\p{\v v} \bk{s | T_{\ell,0} | s},
\end{align}
where
\begin{align}
  \bk{s | T_{\ell,0} | s}
  = \sqrt{\f{2\ell+1}{2s+1}} \, \bk{ss;\ell,0|ss}
  = \sqrt{\f{2\ell+1}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}}
    \p{\f{\p{2s}!}{\p{2s-\ell}!}}},
\end{align}
and the properties of the rotation matrix elements $D^\ell_{mn}$ imply that
\begin{align}
  D^\ell_{0,m}\p{\v v} = \sqrt{\f{4\pi}{2\ell+1}} \, Y_{\ell m}\p{\v v},
\end{align}
so
\begin{align}
  \tilde T_{\ell m}\p{\v v}
  = \sqrt{\f{4\pi}{2s+\ell+1}
    \p{\f{\p{2s}!}{\p{2s+\ell}!}} \p{\f{\p{2s}!}{\p{2s-\ell}!}}} \,
  Y_{\ell m}\p{\v v}.
\end{align}
In this way, the polarization operators are a quantum analogue of spherical harmonics.
